Galaxy Clustering Constraints on the Galaxy Size--Halo Connection

### 2017-08-31 paper/galsize_paper.tex
Improved description of galaxy sample

We additionally use the catalog of SDSS galaxy profile decompositions provided by \citet{meert_etal15}. In the version of this catalog that we use, two-dimensional $r-$band profiles were fit with a two-component de Vaucouleurs + exponential profile for the bulge and disk, respectively. We cross-match our DR10 sample against the \citet{meert_etal15} scale radius of the composite profile, $\rhalf,$ and the $r-$band flux ratio of the two components, $\bt,$ giving us a volume-limited galaxy sample with values of $\mstar,\ssfr,\rhalf,$ and $\bt.$

@@

Together with the present work, we make publicly available this cross-matched catalog, as well as code to generate the catalog from the original data files and load it into a python interpreter.

>>>>

We additionally use the catalog of SDSS galaxy profile decompositions provided by \citet{meert_etal15}. In the version of this catalog that we use, two-dimensional $r-$band profiles were fit with a two-component de Vaucouleurs + exponential profile. We cross-match our DR10 sample against the \citet{meert_etal15} catalog values of $\rhalf,$ the half-light radius of the full profile, and $\bt,$ the $r-$band flux ratio of the de Vaucouleurs component to the total $r-$band flux. This cross-matching gives us a volume-limited galaxy sample with values of $\mstar,$ $\ssfr,$ $\rhalf,$ and $\bt.$ Together with the present work, we make publicly available this cross-matched catalog, as well as code to generate the catalog from the original data files and load it into a python interpreter.

@@
